%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
% 
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[10pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{banking}                             % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
% \renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
% \nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using

\input{glyphtounicode}                             % for export
\pdfgentounicode=1

\usepackage{verbatim}

% adjust the page margins
\usepackage[scale=0.95]{geometry}
\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
% \setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Michael}{Stokley}
% \title{Resumé title}                               % optional, remove / comment the line if not wanted
\address{Seattle, WA}%{postcode city}{country}% optional, remove / comment the line if not wanted; the "postcode city" and "country" arguments can be omitted or provided empty
\phone[mobile]{(303) 801-8575}                   % optional, remove / comment the line if not wanted; the optional "type" of the phone can be "mobile" (default), "fixed" or "fax"
% \phone[fixed]{+2~(345)~678~901}
% \phone[fax]{+3~(456)~789~012}
\email{michael@michaelstokley.com}                               % optional, remove / comment the line if not wanted
\homepage{michaelstokley.com}                         % optional, remove / comment the line if not wanted
\social[linkedin]{mastokley}                        % optional, remove / comment the line if not wanted
% \social[twitter]{jdoe}                             % optional, remove / comment the line if not wanted
\social[github]{mastokley}                              % optional, remove / comment the line if not wanted
% \extrainfo{additional information}                 % optional, remove / comment the line if not wanted
% \photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file

% ----------------------------------------------------------------------------------
% content
% ----------------------------------------------------------------------------------
\begin{document}
% -----       resume       ---------------------------------------------------------
\makecvtitle

\section{Profile}
Software developer. I'm patient enough to take difficult projects seriously, and
driven enough to automate tedious, needlessly manual work. In my previous
accounting position, I greatly exceeded expectations by teaching myself SQL and
relational database theory in order to automate the vast majority of my data
entry and data quality tasks, and avoid using a cumbersome GUI. Since then, I
spent two years studying math, computer science, and statistics at North Seattle
College, attended Code Fellows' Python Development Intensive (taught by esteemed
pythonista Cris Ewing), and have independently studied the classic textbook
\textit{The Structure and Interpretation of Computer Programs}. Recently, I
helped to co-found a local big data/nlp startup, and have been working as a
freelance web developer.

\section{Technical Skills}
\begin{cvcolumns}
  \cvcolumn{Proficient}{Python, Django, Django REST Framework, Pyramid, Git, SQL, HTML/CSS,
    JavaScript/jQuery, Unix systems, Shell Scripting, Org-mode, Regular Expressions}
  \cvcolumn{Familiar}{AWS Deployment, Heroku Deployment, Ansible, PostgreSQL, Nginx, Gunicorn, Scheme, Sed}
\end{cvcolumns}

\begin{comment}
  \section{Technical Skills}
  \subsection{Proficient}
  Python, Django, Django REST Framework, Pyramid, Git, SQL, HTML/CSS,
  JavaScript/jQuery, Unix systems, Shell Scripting, Org-mode, Regular Expressions
  \subsection{Familiar}
  AWS Deployment, Heroku Deployment, Ansible, PostgreSQL, Nginx, Gunicorn, Scheme, Sed
\end{comment}

\section{Experience}

\begin{comment}
  \cventry
  {date - date}
  {Employer}
  {Job Title}
  {}
  {City, State}
  {Description of work
    \begin{itemize}
    \item specific achievement
    \item specific achievement
    \end{itemize}}
\end{comment}

\cventry {2016.08 - present} {Red Mountain Software} {Freelance Web Developer}
{} {Seattle, WA} {Ongoing work to design, build, and test an internal management
  application according to client specification. App built with Django and
  PostgreSQL, with jQuery on the front as needed.
  \begin{itemize}
  \item Designed and implemented database schema
  \item Wrote models, views, and templates
  \item Wrote a method to display arbitrary model fields (including reverse
    relationships) for arbitrary models
  \end{itemize}}

\cventry {2016.07 - 2016.09} {Sternshus, Inc} {Co-founding Software Developer}
{} {Seattle, WA} {Provided front-end solutions in the context of rapidly
  changing business requirements. Worked primarily in Webflow, Django, and
  MySQL. I am most proud of having written sed and python scripts to automate
  merging Webflow files into the larger Django project.}

\cventry {2012.04 - 2015.04} {Cleanscapes} {AR Specialist} {} {Seattle, WA} {
  \begin{itemize}
  \item Wrote and maintained a library of accurate, sophisticated SQL queries
    to capture evolving data inconsistencies; these queries eliminated 37.5
    labor hours per month despite at 126\% increase in customer accounts over
    a two year period
  \item Designed database reports for internal and external customers, such as
    government officials and senior management
  \item Delegated data entry and data revision tasks
  \item Collaborated with operations, data quality, payment processing, and
    customer service teams to analyze and improve processes as new city
    contracts were won
  \end{itemize}}

\section{Projects}

\begin{comment}

  \cventry
  {date}
  {github url}
  {name}
  {}
  {}
  {description}

\end{comment}

\cventry {2016.04}
{\href{https://github.com/homequest/homequest}{github.com/homequest/homequest}}
{HomeQuest} {} {} {A full-stack Python web application to gamify household
  chores and chore management. Manually implemented authorization,
  authentication, and row-level security. Built in Pyramid with a PostgreSQL
  database and deployed on Heroku.}

\cventry {2016.04}
{\href{http://github.com/TeamReciprocity/reciprocity}{github.com/TeamReciprocity/reciprocity}}
{Reciprocity} {} {} {A full stack Python web application for recipe sharing and
  collaboration. Built with Django and PostgreSQL, deployed via Ansible to an
  AWS EC2 instance.}

\cventry {2016.04}
{\href{https://github.com/mastokley/toy_domain_scraper}{github.com/mastokley/toy\_domain\_scraper}}
{Toy Domain Scraper} {} {} {Toy web scraper built in Python. Uses breadth-first
  traversal for fast, reliable results.}

\section{Education}
\cventry {2016} {Certificate} {Code Fellows} {Seattle, WA} {} {Advanced Python
  development emphasizing test driven development, pair programming, agile
  methodologies, version control, and basic data structures and algorithms}

\cventry {2012--2014} {Coursework in Math, Computer Science, and Statistics}
{North Seattle College} {Seattle, WA} {} {}

\cventry {2009} {B. A. in Philosophy} {St. John's College}
{Annapolis, MD} {} {}
% {Double Major: Philosophy and the History of Math and Science\newline{} Double Minor: Classical Studies and Comparative Literature}

\end{document}
